Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
removing unnecessary sentence anymore.
Wording

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

@@

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.

>>>>

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, we think
Python's {\tt doctest} module~\cite{doctest} is interesting.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

@@

Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.
